\documentclass[a4paper,10pt]{article}

\usepackage{parskip} % For spacing between paragraphs
\usepackage{fontspec} % For custom fonts
\usepackage{xcolor} % For colored text
\usepackage{tabularx} % Enhanced tabular environment
\usepackage{enumitem} % For customized lists
\usepackage{titlesec} % For customizing section titles
\usepackage{hyperref} % For clickable links
\usepackage{multicol} % For multiple columns
\usepackage{fontawesome5} % For social icons
\usepackage[normalem]{ulem} % For underlining

% Page margins and layout
\usepackage[scale=0.9, top=.26in, bottom=.1in]{geometry}
% Custom colors
\definecolor{myblue}{HTML}{1C033C}
\definecolor{mydarkblue}{HTML}{371e77}
\definecolor{mylightpurple}{HTML}{4B28A4}
% Configure hyperref to remove link borders
\hypersetup{
    colorlinks=true,      % Enable colored links
    linkcolor=mydarkblue,       % Color for internal links
    citecolor=mydarkblue,       % Color for citations
    filecolor=mydarkblue,       % Color for file links
    urlcolor=mydarkblue,        % Color for URLs
    pdfborder={0 0 0},    % Remove border around links
}


% Custom section formatting
\titleformat{\section}{\Large\scshape\color{myblue}\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}

\newcommand{\sectionheader}[2]{%
    \begin{center}
        \textcolor{myblue}{\Huge #1} \\[6pt]
        \textcolor{mydarkblue}{\underline{\href{#2}{\raisebox{-0.05\height}{\faGithub} GitHub}} $|$}
        \textcolor{mydarkblue}{\underline{\href{https://www.linkedin.com/in/deekshith-bommarthi/}{\raisebox{-0.05\height}{\faLinkedin} LinkedIn}}}
    \end{center}
}

% Custom command for entry in experience section
\newcommand{\experienceentry}[5]{%
    \begin{tabularx}{\linewidth}{@{}l r@{}}
        \color{myblue} \textbf{#1} \hfill \color{mydarkblue} #2 \\[4pt]
        \color{mydarkblue} \textit{#3} \hfill \color{mylightpurple} \textit{#4} \\[5pt]
        \begin{minipage}[t]{\linewidth}
            #5
        \end{minipage}
    \end{tabularx}
}

% Custom section formatting
\titleformat{\section}{\Large\scshape\color{myblue}\centering}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}
% Custom command for section headers with icon
\newcommand{\sectionheader}[2]{%
    \begin{center}
        \vspace*{-\baselineskip} % Adjust vertical space before the section header
        \textcolor{myblue}{\Huge #1} \\[6pt]
        \vspace{-8pt} % Adjust vertical space after the section header
        \textcolor{mydarkblue}{\underline{\href{#2}{\raisebox{-0.05\height}{\faGithub} GitHub}} $|$}
        \textcolor{mydarkblue}{\underline{\href{https://www.linkedin.com/in/deekshith-bommarthi/}{\raisebox{-0.05\height}{\faLinkedin} LinkedIn}}}
    \end{center}
}

% Begin document
\begin{document}

% Title and contact information
% Title and contact information
\begin{center}
    \parbox{\linewidth}{%
        \centering
        \sectionheader{\href{https://deekshith0509.github.io/Portfolio.html}{\textcolor{black}{Deekshith Bommarthi}}}{https://github.com/deekshith0509/} \\[2pt]
        \textcolor{mydarkblue}{\raisebox{-0.05\height}{\faEnvelope} \href{mailto:deekshith.bh0509@gmail.com}{deekshith.bh0509@gmail.com}} $|$ 
        \textcolor{mydarkblue}{\href{mailto:deekshith.bh7878@gmail.com}{deekshith.bh7878@gmail.com}} $|$ 
        \textcolor{mydarkblue}{\raisebox{-0.05\height}{\faMobile} +91 8008565518} \\
    }
\end{center}






\section*{Education}


\begin{tabularx}{\linewidth}{@{} l r @{}}
    \color{myblue} \textbf{Gokaraju Rangaraju Institute of Engineering and Technology, Hyderabad} & \hspace{1.3cm}  \color{mydarkblue} October 2021 - June 2025 \\[1pt] % Added 1pt space
    \color{mydarkblue} B.Tech - Computer Science and Engineering &  \vspace{-10pt}\color{mylightpurple} \textit{GPA: 8.0/10} \\[10pt] % Space between entries
    \color{myblue} \vspace{0pt}\textbf{Vishwa Chaitanya Junior College, Hyderabad} & \color{mydarkblue} June 2019 - June 2021 \\[1pt] % Added 1pt space
    \color{mydarkblue} Intermediate Education - MPC & \color{mylightpurple} \textit{GPA: 9.78/10} \\
\end{tabularx}


% Custom command for skills entry
\newcommand{\skillsentry}[2]{%
    \textcolor{myblue}{\textbf{#1}} & \textcolor{mydarkblue}{#2} \\
}
% Custom command for skills entry
\newcommand{\skillsentry}[2]{%
    \textcolor{myblue}{\textbf{#1}} & \textcolor{mydarkblue}{#2} \\
}
\vspace{-14pt}
% Skills section
\section{Skills}
\begin{tabularx}{\linewidth}{@{} l X @{}}
    \textbf{Languages:} & Python, C, HTML5, CSS3, JavaScript, Bash, SQL. \\
    \textbf{Technologies:} & Git, GitHub, Data Structures and Algorithms, Kivy, KivyMD, Github Actions, Streamlit, Bootstrap, AngularJS, Django, Docker, Telegram-Bot-API, Asyncio, Telethon, GoogleAppsScript, ADB and fastboot, Selenium, Hugging Face Transformers, Pydub, PyInstaller, Termux.  \\
    \textbf{Core Competencies:} & Interactive Web Development, System Automation, API Integration, Application Development. \\
    \textbf{Soft Skills:} & Problem-Solving, Self-Motivation, Project Management, Time Management, Adaptability.  \\
\end{tabularx}

\vspace{11pt}


% Custom command for project entry with button/link
\newcommand{\projectentry}[5]{%
    \noindent\vspace{1pt}
    \textcolor{myblue}{\textbf{\href{#2}{#1}}} \textcolor{mydarkblue}{\href{#3}{\faLink}} \\ \vspace{-10pt}
    \begin{itemize}[left=0pt, label=--, nosep]
        \item \vspace{-10pt}\textbf{Overview:} #4
    % comment    \item \textbf{Languages Used:} #5
    \end{itemize}
    \vspace{-13pt}% Adjust vertical spacing between project details
}

% Projects section with detailed descriptions

\vspace{-13pt}


\section{ \href{https://github.com/deekshith0509?tab=repositories}{Projects}}
\vspace{0pt}
\projectentry
{Kivy Android Application for Cross-Platform File Sharing}
{https://github.com/deekshith0509/Kivy-PyServer}
{https://github.com/deekshith0509/Kivy-PyServer}
{Cross-platform file-sharing application for Windows and Android, enhancing UX over traditional servers:
\begin{itemize}
    \item \textbf{User-Centric Design:} Added directory path input for simpler selection and improved user navigation.
    \item \textbf{Robust File Handling:} Integrated upload and download features for effective file management and sharing.
    \item \textbf{Secure File Access:} Enhanced security by sanitizing file names and managing user access permissions.
    \item \textbf{GitHub Utilization:} Used GitHub Actions for APK creation, demonstrating proficiency in automated workflows.
\end{itemize}}{Python, TensorFlow, Keras, Streamlit.}



\vspace{10pt}

\projectentry
{MetroNavigator-WebApplication}
{https://github.com/deekshith0509/MetroNavigator-WebApp}
{https://github.com/deekshith0509/MetroNavigator-WebApp}
{Django application for metro route visualization and journey planning using Dijkstra's algorithm efficiently.
\begin{itemize}
    \item \textbf{Docker Integration:} Integrates Docker for consistent deployment across multiple environments and platforms.
    \item \textbf{Modern User Interface:} Provides a clean, user-friendly interface designed with Material Design principles.
    \item \textbf{Secure HTTPS Support:} Uses self-signed SSL certificates for secure connections and user data protection.
    \item \textbf{Responsive Layout:} Fully responsive design ensuring optimal functionality on various devices and platforms.
\end{itemize}}




\vspace{10pt}
\projectentry
{Versatile Web Innovations}
{https://deekshith0509.github.io}
{https://github.com/deekshith0509/deekshith0509.github.io}
{Discover my advanced frontend skills through diverse projects designed to enhance user experiences. This repository highlights my expertise across various areas of frontend development and design:
\begin{itemize}
\item \textbf{Frontend Development:} Mastered \textbf{HTML5}, \textbf{CSS3}, and \textbf{JavaScript} for responsive user interfaces.
\item \textbf{Creative Problem Solving:} Developed dynamic storytelling and Tic-Tac-Toe with AI integration for fun.
\item \textbf{User-Centric Design:} Focused on improving user interactions through tools like music players and color generators.
\item \textbf{Efficient Deployment:} Utilized \textbf{Git} and \textbf{GitHub Pages} for seamless version control and management.
\item \textbf{Continuous Learning:} Committed to exploring new technologies to enhance project capabilities and features.
\end{itemize}
}{HTML5, CSS3, JavaScript, jQuery, Bootstrap, AngularJS, Git.}

\vspace{10pt}
\projectentry
{Automated Message Dispatcher}
{https://github.com/deekshith0509/TelegramMessageHub}
{https://github.com/deekshith0509/TelegramMessageHub}
{A robust application designed for cloning group chats and forwarding messages on Telegram:
\begin{itemize}
\item \textbf{Caching and Batch Processing:} Efficiently caches messages and organizes them into JSON files for retrieval.
\item \textbf{API Handling:} Implements robust retry mechanisms to manage API limits and prevent failures.
\item \textbf{Cloning and Forwarding:} Clones group chats while preserving original hierarchy and message structure.
\item \textbf{Real-Time Processing:} Supports cached and direct forwarding, ensuring messages maintain original order.
\end{itemize}
}{} 


\vspace{10pt}
\projectentry
{Advanced Telegram Bots}
{https://github.com/deekshith0509?tab=repositories}
{https://github.com/deekshith0509?tab=repositories}
{Developed Telegram bots for diverse applications, using Python, JavaScript, SQLite, and cryptography:
\begin{itemize}
\item \textbf{\href{https://github.com/deekshith0509/MessageBroadcasting_Bot}{Message Broadcasting Bot:}} Built with \textbf{Python} and \textbf{SQLite}, it facilitates anonymous secret submissions, comments, likes, and broadcasts to subscribed users, ensuring privacy through encrypted storage.
\item \textbf{\href{https://github.com/deekshith0509/WebApplication_Bot}{Web Application Bot:}} Developed using \textbf{JavaScript} and \textbf{Node.js}, it offers functionalities such as weather updates, quizzes, to-do list management, and currency conversion through an Express API and Telegram bot interface.
\item \textbf{\href{https://github.com/deekshith0509/Fileforwardbot}{File Sharing Bot:}} Leveraging \textbf{Python} and \textbf{SQLite}, it manages file uploads in group chats, stores metadata, enables file searching and pagination, and provides admin functions for feedback handling and activity logging.
\end{itemize}
}{Python, SQLite, Telegram Bot API, Cryptography.}
\vspace{10pt}

\iffalse  % Comments Synatx beginning
\projectentry
{Flower Detection using CNN}
{https://github.com/deekshith0509/FlowerDetection}
{https://github.com/deekshith0509/FlowerDetection}
{Developed a CNN-based model for classifying flower species with key features:
\begin{itemize}
\item \textbf{Model Training:} Achieved 90\% accuracy with a CNN trained on a diverse Kaggle dataset, using data augmentation.
    \item \textbf{Interactive Chatbot:} Integrated \textbf{FlowerBot}, increasing user interaction by 50\%.
    \item \textbf{Real-Time Deployment:} Deployed using \textbf{Streamlit}, reducing image recognition time to under 2 seconds.
    \item \textbf{Performance Metrics:} Evaluated using accuracy, precision, recall, improving model reliability by 15\%.
\end{itemize}
}
{Python, TensorFlow, Keras, Streamlit.}

\vspace{10pt}


\projectentry
{Binaries Development Repository}
{https://github.com/deekshith0509/Binary_Development}
{https://github.com/deekshith0509/Binary_Development}
{This repository showcases my ability to create standalone binaries from various types of scripts:
\begin{itemize}
\item \textbf{Binary Creation:} Converts shell scripts and Python code into binaries for easy distribution and use.
\item \textbf{Source Code Security:} Binaries make original source code inaccessible, enhancing security and privacy measures.
\item \textbf{Automation Scripts:} Features tools for web scraping, audio editing, and other daily automation tasks efficiently.
\item \textbf{Diverse Tools:} Continuously updated with a wide range of applications to enhance productivity and workflow.
\item \textbf{Cross-Platform Support:} Provides instructions for using Termux on Android to seamlessly run Linux tools.
\end{itemize}
}{Bash, Python, SHC, PyInstaller, Nuitka, Termux.}

\vspace{8pt}
\fi   % Comments Synatx beginning





% Command for experience entry
\newcommand{\experienceentry}[5]{%
    \begin{tabularx}{\linewidth}{@{} X r @{}}
        \color{myblue} \textbf{#1} & \color{mydarkblue} #2 \\
        \color{mydarkblue} \textbf{#3} & \color{mydarkblue} #4 \\
        \begin{minipage}[t]{\linewidth}
            \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
                #5
            \end{itemize}
        \end{minipage}
    \end{tabularx}
    \vspace{10pt}
}

% Custom section formatting
\titleformat{\section}{\Large\scshape\color{myblue}\centering}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}


% Custom command for entry in coding profiles section
\newcommand{\codingprofileentry}[2]{%
    \textcolor{myblue}{#1 :} \quad \textcolor{mydarkblue}{#2}
}
% Custom command for entry in coding profiles section
\newcommand{\codingprofileentry}[2]{%
    \textcolor{myblue}{#1 :} \quad \textcolor{mydarkblue}{#2}
}
% Command for certification entry
\newcommand{\certificationentry}[2]{%
    \begin{tabularx}{\linewidth}{@{} l X @{}}
        \color{myblue} \textbf{#1} & \href{#2}{\uline{}} \\
    \end{tabularx}
    \vspace{1pt}
}

% Command for listing achievements and activities
\newcommand{\achievements}[1]{%
    \begin{tabularx}{\linewidth}{@{} X @{}}
        \color{myblue} \textbf{Achievements} \\
        \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
            #1
        \end{itemize}
    \end{tabularx}
    \vspace{-10pt}
}

% Command for listing achievements and activities
\newcommand{\activities}[1]{%
    \begin{tabularx}{\linewidth}{@{} X @{}}
        \color{myblue} \textbf{Activities} \\
        \begin{itemize}[nosep, after=\strut, leftmargin=2em, itemsep=2pt]
            #1
        \end{itemize}
    \end{tabularx}
    \vspace{1pt}
}
% Custom section formatting
\titleformat{\section}{\Large\scshape\color{myblue}\centering}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{2pt}{2pt}

% Custom command for section headers with icon
\newcommand{\sectionheader}[2]{%
    \begin{center}
        \textcolor{myblue}{\Huge #1} \\[6pt]
        \textcolor{mydarkblue}{\underline{\href{#2}{\raisebox{-0.05\height}{\faGithub} GitHub}} $|$}
        \textcolor{mydarkblue}{\underline{\href{https://www.linkedin.com/in/deekshith-b-1a09b9297/}{\raisebox{-0.05\height}{\faLinkedin} LinkedIn}}}
    \end{center}
}
\vspace{2pt}
\section{Coding Profiles}

\begin{flushleft}
\begin{tabular}{l l}
    \textbf{Hackerrank} \texttt{:21241A05Z4 (6 Star Rating)} & \textbf{Leetcode} \hspace{17pt}\texttt{:user5777yx (Rating: 1805, 400+ problems)} \\
    \textbf{Codechef}\hspace{14pt}\texttt{:deekshith2124 (Rating: 1565)} & \textbf{Interviewbit} \texttt{:deekshith-b\textunderscore 240 (Score: 24897+)} \\
\end{tabular}
\end{flushleft}
\vspace{-1pt}


\section{ \href{https://certificates7878.glitch.me/}{Certifications}}


\textrm{
\hspace{-3pt}CyberSecurity - Specialization (Coursera),Google Android Developer Internship (AICTE), Full Stack Web Development (Infosys SpringBoard), Data Analytics with Python (NPTEL), Smart-Coder-Diamond (SmartInterviews),SQL Advanced (HackerRank), Software Engineering Intern (HackerRank), ITN-ENSA-SRWE (Cisco). NDG Linux Essentials (Cisco).
}




% Achievements and Activities section
\section{Achievements and Activities}

\vspace{5pt}
\begin{itemize}

    \item Engaged in Smart Interviews for advanced product training and industry knowledge enhancement.\vspace{-5pt}
    \item Competed in major coding contests, demonstrating strong problem-solving and competitive programming skills.\vspace{-5pt}
    \item Achieved over 600 GitHub contributions and developed 15 unique projects using Git and GitHub Actions effectively.\vspace{-5pt}
    
\end{itemize}

\end{document}

